Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-25 manuscript/manuscript.Rmd
mini changes

ppo |> filter(t==max(t))

@@

```{r classical_tuning, fig.cap = "TBD.  Red = MSY, Green = 0.8 TAC", out.width = "6.5in"}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

(rmsy | resc)
```

>>>>

@@

```{r}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

# (rmsy | resc)
```
